\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-06-13 paper/paper.tex
Add citation for depreciation rate

\begin{figure}[H]
\includegraphics[width=.9\textwidth]{fig/data-sum.pdf}
\centering
\caption{Left: Total number of failures (log scale) for drive-models with at least 3 observed failures in the Backblaze data. Right: Total observed time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
\label{fig1}
\end{figure}

@@

While TTF is clearly important, due to the
anticipation of advancements in technology, we can expect that the
relative value of computer hardware will depreciate rather quickly. To account
for this, we can posit a model for this depreciation and instead of
TTF, we can consider the value at replacement. The IRS considered
computer hardware to be ``5-year'' equipment.(form 4562) Using``the declining
balance method'' the rate of depreciation is 40\% per year.

Let $L(t) = e^{-.4t}$ represent the value at the time of failure
relative to its original value. We can then define the predicted loss
of a unit as its value at time of failure.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{fig/dm-eval}
  \caption{Left: Posterior predictive TTF (years) for new
    unit, by drive-model. Right: TTF (top) and loss based on exponential
    devaluation, $\lambda=5$ (bottom), for best 11 drive-models.}
  \label{fig5}
\end{figure}

>>>>

\begin{figure}[H]
  \includegraphics[width=.9\textwidth]{fig/data-sum.pdf}
  \caption{Left: Total number of failures (log scale) for drive-models with at least 3 observed failures in the Backblaze data. Right: Total observed time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
  \label{fig1}
\end{figure}

@@

While TTF is clearly important, due to the
anticipation of advancements in technology, we can expect that the
relative value of computer hardware will depreciate rather quickly. To account
for this depreciation, rather than using TTF as the metric for drive-model comparison, we use the value at replacement. The IRS considers
computer hardware to be ``5-year'' equipment\cite{f4562}. Using``the declining
balance method'' the rate of depreciation is 40\% per year.

Let $L(t) = e^{-.4t}$ represent the value at the time of failure
relative to a new unit. We can rank the drive-models by 
$$\op{E}(L(t_{d,new})|t))\approx \frac{1}{S} \sum_{s=1}^{S} L(t_{d,new}^{(s)}).$$

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{fig/dm-eval}
  \caption{Left: Posterior predictive relative value-at-loss for new
    unit, by drive-model. Right: TTF (top) and VAF based on 40\% annual depreciation (bottom), for best 11 drive-models.}
  \label{fig5}
\end{figure}
